### 2024-08-11 doc/Thesis/chapter/051-results-emma.tex
correct misspellings

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EMMA}
\label{sec:res-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%% ALL SAMPLES
A total of 30 recipes (see appendix \ref{sec:app-emma}) was investigated in 
five iterations ($t = 0, \dots, 4$) of the algorithm. 
Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
The most insulating recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
The experiments for generation 5 where not executed but 
predictions were already made
with the information from the previous generations. 
%%% BEST PREDICTED RECIPE
The sample predicted as optimum by the algorithm is experiment number 13 with 
lowest possible $c_{zr}$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$ and second highest possibel $n_L$ (see table \ref{tab:input}). 
%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
%and lowest calcination heating rate and temperature.

@@

%%% T=4
The coefficients of equations (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) show the same pattern 
as equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}): identical signs and factor 100. 
%The choice of basis functions in combination with their coefficient signs seems more plausible
%for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
%$n_L$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $n_L$ increases the two \textit{optimizands}. 
%
% TCAL ON OPTIMIZANDS
The influence of $T_{cal}$ on the measures of conductance ($\hat\rho$ and $\hat\gamma$) is highly interesting. 
It was expected that 
calcination temperatures under \oc{400} do not suffice to produce compact layers (corresponding to $+h(400-T_{cal})$)
and 
that therefore the resulting layer does not insulate well if $T_{cal}$ is low (under \oc{400}). 
The oppisite is the case, though. % (see figures \ref{fig:g-tcal} and \ref{fig:phd-tcal}).
%This would correspond to $+h(400-T_{cal})$
%The \td{original recipe by Hu et al.\cite{Hu2016} used \oc{500} (but to produce Al2O3, so not a surprise? or?)} and thus even \oc{400} are low.
\textit{Optimizands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
according to equations~(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) (see also figures~\ref{fig:g-tcal} and \ref{fig:phd-tcal}), 
ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.

@@

%%% PROBLEMS 
Even though the main \textit{optimizands} were minimized as required, the \gls{rf}s were not satisfactory. 
The two main problems were too many independent variables and too many dependent variables. 
Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
Too many independent variables make it harder to distinguish variance due to random error (e.g. unmeasured and uncontrolled variables) from variance due to dependency. % of chosen dependent variables. 
The difficulty of identifying meaningful correlation is mainly owed to the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
%
%In the here presented optimization model 
%the data points per independent variable 
%(events per predictor variable EPV) are as low as 5. 
The \gls{epv} (data points per independent varible) are as low as 5 in the here presented optimization. % model and data acquisition method
By eliminating three independent variables the \gls{epv} could rise to 10, which is stated 
as rule of thumb for multivariate regression\cite{vittinghoff2007relaxing}. 
The results obtained with limited sample number deliver remarkable insight %are quite respectable 
comparing to an \gls{epv} of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
and an \gls{epv} of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
%In the original \gls{emma} paper\cite{villanova2010function} the \gls{epv} is 20.
%\td{In the original \gls{mars} paper\cite{friedman1991multivariate} the model is said 
%to work well on 20-50 events per predictor varibale.
%In the current model EPV are around 5, which is even low for a conservative 
%rule of thumbs of 10-15 EPV\cite{vittinghoff2007relaxing}.
%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
%Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
%}
%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EMMA}
\label{sec:res-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%% ALL SAMPLES
A total of 30 recipes (see appendix \ref{sec:app-emma}) was investigated in 
five iterations ($t = 0, \dots, 4$) of the algorithm. 
Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
%The most insulating recipes 
The recipes that produced the most insulating coating for each generation can be seen in table \ref{tab:emma-Gb}. 
The experiments for generation 5 where not executed but 
predictions were already made
with the information from the previous generations. 
%%% BEST PREDICTED RECIPE
The sample predicted as optimum by the algorithm is experiment number 13 with 
lowest possible $c_{zr}$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$ and second highest possible $n_L$ (see table \ref{tab:input}). 
%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
%and lowest calcination heating rate and temperature.

@@

%%% T=4
The coefficients of equations (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) show the same pattern 
as equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}): identical signs and factor 100. 
%The choice of basis functions in combination with their coefficient signs seems more plausible
%for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
%$n_L$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $n_L$ increases the two \textit{optimizands}. 
%
% TCAL ON OPTIMIZANDS
The influence of $T_{cal}$ on the measures of conductance ($\hat\rho$ and $\hat\gamma$) is highly interesting. 
It was expected that 
calcination temperatures under \oc{400} do not suffice to produce compact layers (corresponding to $+h(400-T_{cal})$)
and 
that therefore the resulting layer does not insulate well if $T_{cal}$ is low (under \oc{400}). 
The opposite is the case, though. % (see figures \ref{fig:g-tcal} and \ref{fig:phd-tcal}).
%This would correspond to $+h(400-T_{cal})$
%The \td{original recipe by Hu et al.\cite{Hu2016} used \oc{500} (but to produce Al2O3, so not a surprise? or?)} and thus even \oc{400} are low.
\textit{Optimizands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
according to equations~(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) (see also figures~\ref{fig:g-tcal} and \ref{fig:phd-tcal}), 
ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.

@@

%%% PROBLEMS 
Even though the main \textit{optimizands} were minimized as required, the \gls{rf}s were not satisfactory. 
The two main problems were too many independent variables and too many dependent variables. 
Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
Too many independent variables make it harder to distinguish variance due to random error (e.g. unmeasured and uncontrolled variables) from variance due to dependency. % of chosen dependent variables. 
The difficulty of identifying meaningful correlation is mainly owed to the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
%
%In the here presented optimization model 
%the data points per independent variable 
%(events per predictor variable EPV) are as low as 5. 
The \gls{epv} (data points per independent variable) are as low as 5 in the here presented optimization. % model and data acquisition method
By eliminating three independent variables the \gls{epv} could rise to 10, which is stated 
as rule of thumb for multivariate regression\cite{vittinghoff2007relaxing}. 
The results obtained with limited sample number deliver remarkable insight %are quite respectable 
comparing to an \gls{epv} of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
and an \gls{epv} of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
%In the original \gls{emma} paper\cite{villanova2010function} the \gls{epv} is 20.
%\td{In the original \gls{mars} paper\cite{friedman1991multivariate} the model is said 
%to work well on 20-50 events per predictor varibale.
%In the current model EPV are around 5, which is even low for a conservative 
%rule of thumbs of 10-15 EPV\cite{vittinghoff2007relaxing}.
%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
%Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
%}
%

### 2024-08-11 doc/Thesis/chapter/052-post-emma.tex
correct misspellings

%
Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $n_L$ are largest in value, but the values which are factored with these coefficients - i.e.\, $c_{zr}$ and $n_L$ themselves -- are the smallest among the input variables. 
Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
For better comparison, the influence of an input variable was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{i,min}+x_{i,max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression. 
%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{C}$. 
The biggest influence on $\hat\rho$ is  $n_L$, followed by $T_{cal}$. 
While $T_{cal}$ is the second largest influence on $\hat\rho$ as well, it is noteworthy that $n_L$ contributes the least to $\hat\gamma$. 
That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artefact of the noise rather than a process property. 
%Furthermore the influence on $\hat\rho$ is dominated by $n_L$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
%Different distributions were not expected. 
The two very different distributions of influence among the input variables can have three reasons:
%This can have two reasons: 
(1) the linear function is not a suitable regression function for the data distribution.
(2) the signal to noise ratio is so low that the noise rather than the signal was fitted.
(3) the \textit{optimizands} indeed represent different properties of the material.
%either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
%

>>>>

%
Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $n_L$ are largest in value, but the values which are factored with these coefficients - i.e.\, $c_{zr}$ and $n_L$ themselves -- are the smallest among the input variables. 
Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
For better comparison, the influence of an input variable was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{i,min}+x_{i,max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression. 
%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{C}$. 
The biggest influence on $\hat\rho$ is  $n_L$, followed by $T_{cal}$. 
While $T_{cal}$ is the second largest influence on $\hat\rho$ as well, it is noteworthy that $n_L$ contributes the least to $\hat\gamma$. 
That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artifact of the noise rather than a process property. 
%Furthermore the influence on $\hat\rho$ is dominated by $n_L$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
%Different distributions were not expected. 
The two very different distributions of influence among the input variables can have three reasons:
%This can have two reasons: 
(1) the linear function is not a suitable regression function for the data distribution.
(2) the signal to noise ratio is so low that the noise rather than the signal was fitted.
(3) the \textit{optimizands} indeed represent different properties of the material.
%either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
%

### 2024-08-11 doc/Thesis/chapter/053-discussion.tex
rename to fit numbering
change lambda to n_L
correct misspellings

\section{Hindsight is easier than foresight}
\label{sec:res-discussion}
%\section{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%\todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%\todo{british or US?: zation vs zation} 
%\todo{ include last phase into previous section}
This section will discuss mistakes, improvements and lessons learned from each phase of this project. % in chronological order. 
Firstly,
the "\nameref{sec:phase1}" will be discussed in subsection \ref{sec:phase1}, 
followed by the "\nameref{sec:phase2}" reviewd in subsection \ref{sec:phase2} 
%, thereupon the 
and finally the "\nameref{sec:phase3}" examined in subsection \ref{sec:phase3}.
%\ref{sec:phase3} \textit{\nameref{sec:phase4}}%
% will be discussed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research, exploration and design phase}
\label{sec:phase1}
%\td{freewriting}: 
\textbf{Scrutinize everything!} At the beginning of a project it is important 
to get a ``feel''. 
I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that 
improving the recipe still lead to poor performance.
%no matter how much I improved it, it was still bad. 
This was only noticed after trying out another recipe. 
The author's tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever can be. 
This will 
make it possible to acquire 
%get you a 
``feel'' of what works and what does not. 
%Thinking back to some design classes I took with \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir} for data visualization: 
This is inspired by a quote from \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir}'s 
data visualization classes: ``create as many and different designs as possible''.
One should check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

@@

This leads to more information which can be extracted from the same amount of data, 

@@

\subsection{Optimization, modelling and data generation phase}

@@

    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 

>>>>

\section{Hindsight is easier than foresight}
\label{sec:res-discussion}
%\section{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%\todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%\todo{british or US?: zation vs zation} 
%\todo{ include last phase into previous section}
This section will discuss mistakes, improvements and lessons learned from each phase of this project. % in chronological order. 
Firstly,
the "\nameref{sec:phase1}" will be discussed in subsection \ref{sec:phase1}, 
followed by the "\nameref{sec:phase2}" reviewed in subsection \ref{sec:phase2} 
%, thereupon the 
and finally the "\nameref{sec:phase3}" examined in subsection \ref{sec:phase3}.
%\ref{sec:phase3} \textit{\nameref{sec:phase4}}%
% will be discussed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research, exploration and design phase}
\label{sec:phase1}
%\td{freewriting}: 
\textbf{Scrutinize everything!} At the beginning of a project it is important 
to get a ``feel''. 
I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that 
improving the recipe still lead to poor performance.
%no matter how much I improved it, it was still bad. 
This was only noticed after trying out another recipe. 
The author's tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever can be. 
This will 
make it possible to acquire 
%get you a 
``feel'' of what works and what does not. 
%Thinking back to some design classes I took with \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir} for data visualization: 
This is inspired by a quote from \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir}'s 
data visualization classes: ``create as many and different designs as possible''.
One should check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

@@

This leads to more information, which can be extracted from the same amount of data, 

@@

\subsection{Optimization, modeling and data generation phase}

@@

    \item why $\gamma ~ n_L$? (minimum for layer count?) according which eq? emma? 

### 2024-08-11 doc/Thesis/chapter/06-outlook.tex
change lambda to n_L
correct misspellings

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel blade coating process resulting in an exlectrical insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photovoltaics. 
The ceramic needs to be homogeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and adapted. 
The recipe was improved by increasing the stability of the solution. 
The process variables were optimized via \gls{emma}. 
%\td{ALSO: How many exp would you over the computer time and effort to find this out?}
The best parameters found by the \gls{emma} optimization were 
$c_{zr}=2$, $\lambda=10$, $v_{C}=10$, $T_{C}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimization, the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparison of methods showed that \gls{emma} performed well on identifying the important correlation between conductance and process variables. 
%was wurde herausgefunden? 
A correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
Furthermore, the layer count has been verified as an important factor. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of conductance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

>>>>

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel blade coating process resulting in an electrical insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photovoltaics. 
The ceramic needs to be homogeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and adapted. 
The recipe was improved by increasing the stability of the solution. 
The process variables were optimized via \gls{emma}. 
%\td{ALSO: How many exp would you over the computer time and effort to find this out?}
The best parameters found by the \gls{emma} optimization were 
$c_{zr}=2$, $n_L=10$, $v_{C}=10$, $T_{C}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimization, the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparison of methods showed that \gls{emma} performed well on identifying the important correlation between conductance and process variables. 
%was wurde herausgefunden? 
A correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
Furthermore, the layer count has been verified as an important factor. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of conductance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
